Token-level author diarization using clustering of stylistic contexts

### 2017-05-30 paper/paper.tex
gitignore

Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$. Let $(\mathbf{t}_i)_{i=1}^n =  f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n) = (T(\mathbf{b}_i))_{i=1}^n$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.

>>>>

Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$. Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
